### 2018-01-23 mcmc.tex
tweak

In what follows, we are going to provide a kind of ``user manual'' or
advice document or folklore capture regarding the use of \MCMC\ for
data analysis.
This will not be a detailed description of multiple \MCMC\ methods
(indeed, we will only explain one method in detail), and it will not
be about the mathematical properties or structure of the method or
methods.\note{For a description of various different sampling methods,
  given from the point of view of an astrophysicist, see the review by
  \citet{sharma}. We say a bit about different \MCMC\ methods in
  \sectionname~\ref{sec:methods}, but our discussion is limited
  relative to Sharma's review. For even more depth, there are relevant
  book-length treatments of \MCMC; our favorite is \citet{mcmchandbook}.
  There are also
  good books on Bayesian data analysis more generally that
  include discussion of \MCMC\ as a part of that;
  for example, \citet{kruschke}, and \citet{andreon} and \citet{hilbe}.}
Think of this \documentname\ as a getting-started document for a new user
of \MCMC\ methods.
It concentrates on conceptual points, and questions we get asked
frequently by users, with a concentration on how an \MCMC\ project is
diagnosed and tested, and how its outputs are used responsibly.
Most of what we say will
be applicable to any \MCMC\ method; in that sense the discussion is general.
And all in the language---more-or-less---of an astrophysicist.

>>>>

In what follows, we are going to provide a kind of ``user manual'' or
advice document or folklore capture regarding the use of \MCMC\ for
data analysis.
This will not be a detailed description of multiple \MCMC\ methods
(indeed, we will only explain one method in detail), and it will not
be about the mathematical properties or structure of the method or
methods.\note{For a description of various different sampling methods,
  given from the point of view of an astrophysicist, see the review by
  \citet{sharma}. We say a bit about different \MCMC\ methods in
  \sectionname~\ref{sec:methods}, but our discussion is limited
  relative to Sharma's review. For even more depth, there are relevant
  book-length treatments of \MCMC; our favorite is \citet{mcmchandbook}.
  There are also
  good books on Bayesian data analysis from a computing perspective more generally that
  include discussion of \MCMC\ as a part of that;
  for example, \citet{kruschke} and \citet{andreon} and \citet{hilbe}.}
Think of this \documentname\ as a getting-started document for a new user
of \MCMC\ methods.
It concentrates on conceptual points, and questions we get asked
frequently by users, with a concentration on how an \MCMC\ project is
diagnosed and tested, and how its outputs are used responsibly.
Most of what we say will
be applicable to any \MCMC\ method; in that sense the discussion is general.
And all in the language---more-or-less---of an astrophysicist.
